Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-14 paper.tex
author list

\author{Mathieu Blondel\inst{1} \and
        Lars Buitinck\inst{2} \and
        Gilles Louppe\inst{3} \and
        Jake Vanderplas\inst{4}}

\institute{Graduate School of System Informatics, Kobe University \and
           Informatics Institute, University of Amsterdam \and
           Department of EE \& CS, University of Liège \and
           Astronomy Department, University of Washington}

>>>>

\author{Lars Buitinck~\inst{1,2} \and
        Gilles Louppe~\inst{1,2} \and
        Mathieu Blondel~\inst{1,2} \and
        Fabian Pedregosa~\inst{2} \and
        Andreas Mueller~\inst{2} \and
        Gaël Varoquaux~\inst{2} \and
        Olivier Grisel~\inst{2} \and
        Vlad Niculae~\inst{2} \and
        Peter Prettenhofer~\inst{2} \and
        Alexandre Gramfort~\inst{2} \and
        Jacques Grobler~\inst{2} \and
        Robert Layton~\inst{2} \and
        Jake Vanderplas~\inst{2} \and
        Arnaud Joly~\inst{2} \and
        Bernard Thirion}

\institute{Main authors of the present paper \and
           Core contributors to the project}
